\problemname[stdin/stdout]{Modelling Viruses}
\htodo{Eduard, check the statement}
You have been asked to write a program to model the spread of a virus in a population.
As an excellent programmer, you have split the task into simple sub-tasks.
In your current sub-task you model the movement of two people, Alice and Bob.
Your goal is to determine if they violate the social-distancing rules, and if so, when.
\htodoi{alternative: Your goal is to determine if they have a chance of infecting one another, and if so, when.}
%Your goal is to determine if the distance between Alice and Bob is $2$ meters or less, during an interval of $T$ seconds.

Alice and Bob are represented as points moving in the two dimensional space.
Alice starts her movement at point $A$ at time $0$ and
moves with a constant velocity given by a vector $v_A$.
You have the same information about Bob.
%, given by the point $B$ and velocity vector $v_B$.
Both Alice and Bob move for exactly $T$ seconds, and then stop.

%Alice and Bob have a chance to infect one another if their distance becomes $2$ metres or less.
%Write a program that finds the earliest time when they have a determines if Alice and Bob are ever $2$ meters or less away from one another.\htodo{have a look at the new statement).
Alice and Bob violate the social-distancing rule if their distance is $2$ metres or less.
Write a program that determines the earliest time when they violate the rule, if they ever do.

\section*{Input}
\htodo{What samples should we include? Many different cases, or no?}
The first line of the input contains a single integer $T (1 \leq T \leq 10^5)$, the length of the time interval of interest.
The second line contains the information about Alice, four space-separated integers $x, y, v_x, v_y$,  which are all at most $10^5$ in absolute value.
The starting position of Alice is $A = (x, y)$ and her velocity is given by the vector $v_A = (v_x, v_y)$.
The third line contains the information about Bob, in the same format and satisfying the same conditions.
All the values are in standard units, i.e., metres and seconds.

\section*{Output}
The only line of the input should have the first time, in seconds,
when Alice and Bob are violating the social-distancing rule.
If this never happens, simply output $-1$.
Your output should have $5$ digits after the decimal point.
%when Alice and Bob are at most $2$ meters apart during the $T$ seconds of their movements.
%If this does not happen, simply output $-1$.
%Your output should have $5$ digits after the decimal point.
%\htodoi{A different option for this problem: Alice and Bob's movement is given by $K$ line segments (bekyal). And they move at a constant velocity. Do they meet ? }
