\problemname{Roman Road}
% Author: Hayk Saribekyan

The towns of Cowford and Wentbridge are connected by an old one-way Roman road.
The roads that Romans built were very straight, so we will represent the road between Cowford and Wentbridge as the $x$-axis, where Cowford is at coordinate $0$ and Wentbridge is at coordinate $L$.

The Roman roads were not designed for cars, so some cars cannot pass one another.
In particular, if a faster car of width $w_F$ approaches a slower car of width $w_S$, then the faster car can only overtake if $w_F + w_S \leq W$.
Otherwise, the faster car is stuck behind the slower one and the two cars have to drive at the same speed.
\htodo{do we need to say that cars are points?}
\htodo{maybe we could give the cars lengths too?}

On the weekend, the $n$ residents of Cowford go to Wentbridge in their cars.
Resident $i$ leaves Cowford at time $t_i$, and moves at speed $s_i$ meters per second towards Wendbridge, along the Roman road.
Additionally, the width of the car of resident $i$ is $w_i$.

As the administrator for the Roman roads, your goal is to determine the order in which the residents of Cowford arrive to Wentbridge.

\section*{Input}
The first line of the input contains three integers: $n$ ($1 \leq n \leq 10^5$), the number of Cowford residents; $L (1 \leq L \leq 10^9)$ the length of the Roman road in meters; $W (1 \leq W \leq 10^7)$ the width of the roads in microns.

Line $i$ of the input after that contains three integers: $t_i (0 \leq t_i \leq 10^9)$\htodo{given the time or the initial coordinates}, the time resident $i$ left Cowford; $s_i (1 \leq s_i \leq 10^9)$, the speed at which that resident travels in meters per second; $w_i$ ($1 \leq w_i \leq W)$, the width of the $i$th resident's car.

\section*{Output}
\htodoi{What is the output? Three options: (1) a permutation of $n$ integers, the order the cars arrive; (2) the time when each one arrives; (3) the time when the last one arrives.

(1) is not unique so, (1.1) If a is stuck behind b, they are at the same location, but b always arrive before a; (1.2) Return in lexicographic order; (1.3) arbitrary order - need a checker.

I like (1.1) most but still not unique and maybe explaining is hard? Also the code is a bit more tricky maybe.

Maybe (1.1) + lexicographic, so we do not need a checker?

Actually doesn't lexicographics => (1.1)?
}
