\problemname[interactive]{Guess the Number}
This is an interactive problem.
Your program will interact with the one written by the jury using the standard input and output.
The jury’s program is given a hidden integer $h$ between $1$ and $n$ ($1 \leq n \leq 10^6$).
The goal of your program is to guess $h$ in at most $100$ attempts.
You make attempts and the jury's program replies whether your guess is larger, smaller or equal to the given number.

\paragraph{The interaction protocol.}
First, your program needs to read the number $n$ from the first line of the standard input.
Then your program should print its guess attempt $x$ in the standard output.
$x$ must be an integer between $1$ and $n$.
Then your program reads the jury’s program’s response from one line of the standard input.
You may get one of the following inputs:
\begin{itemize}
    \item $-1$ -- this means that $h < x$, i.e., the hidden number is smaller than your guess;
    \item $1$ -- this means that $h > x$, i.e., the hidden number is larger;
    \item $0$ -- this means that the hidden number and your guess are equal.
\end{itemize}
When your program finds the hidden number or receives EOF (end-of-file) signal, it must quit its execution.
Do not forget to flush after each output.
See the last page for more details about interactive problems.

\paragraph{Limits.}
The number $n$ is between $1$ and $10^6$, and your program must find the answer in at most $100$ attempts.

\emph{Note, in the examples below, the empty lines are only for presentation.
Your program must not produce them.}
{
\renewcommand{\sampleinputname}{Jury's feedback}
\renewcommand{\sampleoutputname}{Your attempts}
\displaysample{../problems/practice-guess-the-number-interactive/tests/sample1}
\displaysample{../problems/practice-guess-the-number-interactive/tests/sample2}
}
