\problemname[output-only]{Formula One}
As we already know, Eduard likes to look at and collect statistics very much.
And he also is a \href{https://en.wikipedia.org/wiki/Formula_One}{Formula One} fan.
So he decided to collect his personal list of F1 results from different years and races.
Eduard only cares about The Grands Prix, which is a series of races that take place across the world throughout the year.

He prepared a list of questions about the information he is missing in one file:
\href{http://ejudge.rau.am/ejudge/formula1.txt}{formula1.txt}.
Help him to find the answers.
\htodoi{Question reformat: Which company was at position 4 in race 3 of 1960 F1 Grands Prix?}
%
%First he prepared a list of all data requests that he needs to pull and started to pull data from Wikipedia.
%He did for the first 5 requests, but got tired after that, because it was taking too long.
%
%Now Eduard asks you for the help.
%You can find the list of all the requests here \href{http://ejudge.rau.am/ejudge/formula1.txt}{Formula1.txt}.

\section*{Input}
There is no input for this problem, except for the link above.
Here is an \href{http://167.71.248.201/ejudge/formula1.txt}{alternative link} to the page.
\htodo{the links do not work}

\section*{Output}
You should simply upload or paste list of companies that took the corresponding place on the given round of the give year.
Your output must have 482 lines.

Below are the first $5$ lines of the output in the correct format:
\begin{center}
    \begin{tabular}{l}
        \texttt{Ferrari} \\
        \texttt{Arrows} \\
        \texttt{McLaren} \\
        \texttt{Mercedes} \\
        \texttt{Tyrrell}
    \end{tabular}
\end{center}
