\problemname[output-only]{Can you unzip me?}
To spend lockdown period effectively Eduard decided to clean his computer's hard disc from unneeded files.
He knew that there are lot of unneeded files, but he never expect to find a file called ``big.txt'' of ~500 GB size.
He tried to open the file, but the text editor crashed :)
He can't remember how this file was created and why it was created.
But fortunately there was another file called ``small.txt'' next to it, which he was able to open using a text editor.
This file was full of whitespace, but contained a hidden phrase somewhere in the middle of the file.

So Eduard understands that there is a hidden text among the whitespaces in the ``big.txt'' file as well and was able to find the hidden text after that.
After that Eduard decided to keep both files, but zip them to save space.
He zipped files, and then zipped resulted .zip files once more (double zipping).
Then he decided to challenge his friend Hayk and sent him the resulted zip files and asked to find the hidden phrases.
Hayk was able to find phrase from ``small.txt'' and it was "happy\_new\_year".
But he needs your help for finding the hidden phrase in ``big.txt''.

You can download both files by the following links.

\begin{center}
    \href{http://167.71.248.201/ejudge/small.zip}{small.zip}
    
    \href{http://167.71.248.201/ejudge/big.zip}{big.zip}
\end{center}

\section*{Input}
There is no input for this problem, except for the zip files above.

\section*{Output}
You should simply upload or paste the hidden phrase of ``big.txt'' file in the online judge, on a single line.
